Active Type Constructors

### 2014-06-04 atlang-gpce14/atlang-gpce14.tex
atlang-gpce14 submission
static in subtitle

\title{Active Type Constructors}
\subtitle{Unambiguously Growing a Type System Inside a Python}
%\titlebanner{{\tt \textcolor{Red}{{\small Under Review -- distribute within CMU only.}}}}        % These are ignored unless
%\preprintfooter{Distribute within CMU only.}   % 'preprint' option specified.

@@

\begin{codelisting}[t]
\begin{lstlisting}
from listing1 import fn, dyn, Account, Details, 
  log_transfer
import datetime
@fn[dyn, dyn]
def pay_oopsie(memo):
  if datetime.date.today().day == 1: # @lang to Python
^\label{error-start}^    account = {nome: "Oopsie Daisy", 
      account_num: "0-00000000"} [:Account] # (format)
    details = {amount: None, memo: memo} [:Details]
    details.amount = 10 # (immutable)
    log_transfer((account, details)) # (backwards) ^\label{error-end}^
print "Today is day " + str(datetime.date.today())
pay_oopsie("Hope this works..") # Python to @lang
print "All done."
\end{lstlisting}
\caption{[\texttt{listing\ref{oops}.py}] Lines \ref{error-start}-\ref{error-end} each have a type error.}
\label{oops}
\end{codelisting}
\begin{codelisting}[t]
\begin{lstlisting}[style=Bash]
$ `python listing^\color{blue}\ref{oops}^.py`
Today is day 2
Traceback (most recent call last):
  File "listing^\ref{oops}^", line 9, in <module>
atlang.TypeError: 
    File "listing^\ref{oops}^.py", line ^\ref{error-start}^, col 12, in <module>: 
      [record] Invalid field name: nome
\end{lstlisting}
\caption{Execution never proceeds into a function with a type error.}
\label{oops-exec}
\end{codelisting}

>>>>

\title{Active Type Constructors}
\subtitle{Unambiguously Growing a Static Type System Inside a Python}
%\titlebanner{{\tt \textcolor{Red}{{\small Under Review -- distribute within CMU only.}}}}        % These are ignored unless
%\preprintfooter{Distribute within CMU only.}   % 'preprint' option specified.

@@

\begin{codelisting}[t]
\begin{lstlisting}
from listing1 import fn, dyn, Account, Details, 
  log_transfer
import datetime
@fn[dyn, dyn]
def pay_oopsie(memo):
  if datetime.date.today().day == 1: # @lang to Python
^\label{error-start}^    account = {nome: "Oopsie Daisy", 
      account_num: "0-00000000"} [:Account] # (format)
    details = {amount: None, memo: memo} [:Details]
    details.amount = 10 # (immutable)
    log_transfer((account, details)) # (backwards) ^\label{error-end}^
print "Today is day " + str(datetime.date.today())
pay_oopsie("Hope this works..") # Python to @lang
print "All done."
\end{lstlisting}
\caption{[\texttt{listing\ref{oops}.py}] Lines \ref{error-start}-\ref{error-end} each have a type error.}
\label{oops}
\end{codelisting}
\begin{codelisting}[t]
\begin{lstlisting}[style=Bash]
$ `python listing^\color{blue}\ref{oops}^.py`
Today is day 2
Traceback (most recent call last):
  File "listing^\ref{oops}^", line 9, in <module>
atlang.TypeError: 
    File "listing^\ref{oops}^.py", line ^\ref{error-start}^, col 12, in <module>: 
      [record] Invalid field name: nome
\end{lstlisting}
\caption{Execution never proceeds into a function with a type error when using @$\texttt{lang}$ for implicit compilation.}
\label{oops-exec}
\end{codelisting}
